What covert verbal actions tell us about the interplay between language, action, and perception

### 2021-06-07 manuscript.tex
minor updates to introduction

\noindent Humans have a remarkable ability to imagine actions without executing them. Such motor imagery is accompanied by a subjective multi-sensory experience with auditory, visual, and kinaesthetic components. An influential hypothesis states that these sensory percepts result from a simulation of the corresponding motor action that relies on the same internal models recruited for the control of overt actions. A significant consequence of this hypothesis is that the sensory experience of covert actions would be continuously shaped by sensorimotor interactions with the environment. However, the precise computations required by these internal models and their neural implementation remain unclear. Moreover, this simulationnist view raises the question of how it is possible to imagine actions without executing them. In this perspective, we focus on covert verbal actions such as covert speech, writing, or typing, as an exciting case study to help understanding the interplay between language, motor control, and perceptual processes.

@@

\tiny
 \keyFont{\section{Keywords:} motor imagery, covert speech, motor simulation, motor control, response inhibition} % All article types: you may provide up to 8 keywords; at least 5 are mandatory.
\end{abstract}

@@

The ability to mentally examine our thoughts is central to our subjective experience. Mentally anticipating or rehearsing (verbal) actions allows us to become better at performing them \citep[e.g.,][]{toth2020}, to explore novel situations \citep{babar}, or to ... \citep{babar}. Broadly construed, motor imagery can be defined as the mental process by which one rehearses an action without engaging in the physical movements involved in this particular action. Because speech production results from sequences of motor commands that are assembled to reach a given communication goal, it belongs to the broader category of motor actions \citep{jeannerod_motor_2006}. Therefore, a parallel can be drawn between covert speech (also known as \textit{inner speech} or \textit{speech imagery}) and other forms of covert verbal actions (e.g., covert signing, covert writing, covert typing) and, more generally, of motor imagery \citep{alderson-day_inner_2015, perrone-bertolotti_what_2014, loevenbruck_cognitive_2018}.

One of the most influential theoretical model of motor imagery the motor simulation theory \cite{jeannerod_origin_2006, jeannerod_representing_1994, jeannerod_neural_2001}, postulates the existence of a continuum between the covert and the overt execution of an action and that action representations can operate off-line via a simulation mechanism. In short, covert actions would rely on the same set of mechanisms as the overt actions they simulate, except that execution is inhibited \citep{oshea_does_2017}. A second class of models are concerned with the phenomenon of emulation \citep{grush_emulation_2004} and with internal models \cite[for a review of the similarities and dissimilarities between simulation and emulation models, see][]{gentsch_towards_2016}. Internal model theories share the postulate that action control uses internal models, that is, systems that simulate the behaviour of the motor apparatus \citep[e.g.,][]{jordan_forward_1992, kawato_hierarchical_1987}. The function of internal models is to estimate and anticipate the outcome of a motor command. Among the internal model theories, motor control models based on robotic principles \citep[e.g.,][]{kawato_internal_1999, wolpert_internal_1995} assume two kinds of internal models: a forward model (or simulator) that predicts the sensory consequences of motor commands from efference copies of the issued motor commands, and an inverse model (or controller) that calculates the feedforward motor commands from the desired sensory states \citep{gentsch_towards_2016, loevenbruck_cognitive_2018}. Notice that in the following, we do not distinguish further between simulation and emulation, and we use these terms interchangeably to designate the mechanism through which sensory consequences of motor commands (or copy thereof) are computed by forward internal models.

@@

In this perspective, we explore some theoretical and experimental consequences of considering covert verbal actions (e.g., covert speech, covert typing) as inhibited verbal actions. We explore two main themes. First, we discuss the plausible origins of the multisensory (e.g., auditory, kinaesthetic) content of covert verbal actions. Second, we discuss the under-explored role of inhibitory mechanisms during motor imagery and covert verbal actions more specifically. By bridging together recent results from motor imagery, motor inhibition, and inner speech research, we highlight some novel and possibly fruitful lines of research.

@@

How does motor learning/experience influence the multisensory content/experience of motor imagery and covert verbal actions? In other words, how to the motor and perceptual system interact during covert verbal actions? In the first subsection, we discuss two mechanisms that may be responsible for providing the sensory content of covert verbal actions and their respective involvement and delimitation. In the second subsection, we discuss an exciting avenue for investigating the influence of motor learning on the sensory content of imagined actions, namely studying the imagery of totally novel (i.e., never executed) actions...

@@

The production of covert speech is often accompanied by the feeling of hearing speech. In this section, we discuss a theoretical account of the mechanisms leading to the generation of these percepts during covert speech, while noticing that these mechanisms could be extended to other forms of covert verbal actions as well.

Where does this sensory (e.g., auditory) content dome from? Prediction-by-simulation or prediction-by-association \citep{pickering_integrated_2013}? Direct simulation (attention-guided memory retrieval process) or indirect simulation (motor simulation process) \citep{tian_mental_2012, tian_effect_2013, li_corollary_2020, ma_distinct_2019}? The dual stream prediction model \citep{tian_mental_2016}...

The balance between these two mechanisms may depend by the precise instructions given to the participants... More precisely, depending on whether they are instructed to "imagine speaking" or "imagine hearing" speech (similar to the distinction between the "inner ear" and the "inner voice", e.g., \cite{smith_subvocalization_1992})... distinct MEG correlates and effects on a subsequent categorisation task \citep{ma_distinct_2019}...

Memoisation: avoid redundant computation by storing computational results and reusing them later... functions call are intercepted with by a memoiser the inspects the previous calls of a function and its outputs. If a function has already been called with the same input, then the previously computed output is retrieved and reused... memoisation can be made more flexible (generalisable) by using \textit{interpolation} between cached outputs... for instance, in the context of motor control, reaching a goal (e.g., a cup of tea) can be decomposed in motor primitives, where input-output mapping can be retrieved from a memo table and/or interpolated from sufficiently similar stored mappings... or as put by \cite{dasgupta_memory_2021}, the "shift from algorithm to memory"... this shift is consistent with studies showing a lesser involvement of the motor system for well known imagined actions... Depending on whether the task needs to form "precise" sensory representations and whether we have the time resources to do it... training studies also suggest that we rely more and more on domain-general memory-processed with expertise \cite{tarr_mental_1989, jolicoeur_time_1985}...

In the absence of non-ambiguous instructions, and in line with \cite{tian_mental_2012}, we suggest that the balance between these two mechanisms may depend on situational (e.g., surrounding noise) and intrinsic (e.g., expertise) characteristics. In addition to \cite{tian_mental_2012}, we suggest that a common currency determining the use of one of these mechanisms is the computational cost/resource of either alternative. To clarify, we ... the concept of memoisation as applied to cognition and mental imagery \citep{dasgupta_memory_2021}. In this context, memory can be considered as a mechanisms to facilitate computational reuse. In the same way... efficient cognition may relies on stored past computation results rather than reinventing the wheel every time. In the context of motor and speech imagery... In other words, situational (extrinsic) and individual (intrinsic) characteristics jointly determine the computational cost (or equivalently, the available computational resources), which in turn determines the balance between the simulation and association mechanisms. Novel and/or difficult tasks may rely more on the simulation mechanism whereas well known tasks may rely more on associative mechanisms... See also the discussion in \citep{nalborczyk_understanding_2019-1, nalborczyk_re-analysing_2020}.

@@

A prediction of this putative mechanism is that the imagination of novel actions, and more precisely, the predicted sensory consequences of novel actions, may be "biased" or "constrained" by the repertoire of already-known actions, given that internal models were developed based on precisely the repertoire of already-known actions. This prediction could be assessed by asking participants to imagine a novel action and subsequently checking whether this improves the execution of an intermediate (interpolated) novel action in the articulatory space. The same logic could be applied to the covert production of speech with someone else’s voice. How can we imagine speaking with the voice of our relatives? If it is based on simulators (i.e., on internal models), then the covert production of speech with someone else’s voice should possess sensory properties that are somehow "biased" or "constrained" by the properties of our own sensory and motor systems. Taking as an illustration the auditory sensations of speech, the subjective auditory sensation of covert speech with someone else’s voice should be situated in a somehow intermediate location in the auditory (e.g., formantic) space between the acoustic properties of our own voice and the acoustic properties of someone else voice.

@@

The proposal that overt and covert actions share common neural circuits is faced with a serious problem. If the neural circuits used for the control of overt actions are reused for covert actions, how can covert actions not lead to execution? This puzzle, coined as \textit{the problem of inhibition} by \cite{jeannerod_neural_2001}, can be rephrased as follows: given the putative role of the motor system in providing the multisensory content of motor imagery, how is it possible for motor imagery not to lead to motor execution? In the following, we briefly summarise the evidence in favour of the view of covert verbal actions as inhibited verbal actions. Then, we discuss the relations between this view and the presumed progressive internalisation of speech during childhood. Finally, we outline some working hypotheses regarding the cognitive and neural implementation of these inhibitory mechanisms \textit{(and their plausible roles in psychological disorders)}.

@@

More detailed categorisation of inhibitory mechanisms can occur at any location in this three-dimensional space but for the current purpose it is sufficient to say that we are interested (purportedly) in an intentional (we know we want to produce motor imagery rather than overt execution) but automatic (we do not explicitly think about not producing movements), planned ahead (proactive), and possibly global form of response inhibition... or maybe both global and effector-specific, cf. the results of \cite{rieger_inhibition_2017}...

Inhibitory mechanisms underlying the ability to imagine actions \citep{guillot_imagining_2012, schwoebel_man_2002}... mentioning the success of BCI with neural activity recorded in premotor/motor areas durmong motor imagery and silent speech... Neural correlates... the inhibitory triangle (cf. Figure \ref{fig:2}), composed of the preSMA, the rIFC, and the STN... A functional dissociation between the preSMA and the rIFC \citep{diesburg_pause-then-cancel_2021}... Moreover, they also reported a reduced short-interval intracortical inhibition (SICI) in patients with TS, a phenomenon that has been shown to be involved in response inhibition during motor imagery \citep{neige_unravelling_2020}...

Inhibition or subliminal activity/bypassing? \citep{tian_mental_2012, tian_effect_2013, tian_mental_2016} vs. \cite{loevenbruck_cognitive_2018}... However, stating that motor imagery only involve subthreshold activity (and therefore is not accompanied by the emission of motor commands that to be inhibited) simply shifts the problem from "how and where motor commands are subsequently inhibited" to "how and where the magnitude of activity in the motor system is planned". In other words, we still need to explain how (in a mechanistic and/or developmental way) this activity is maintained at a subthreshold level. What cognitive and neural mechanisms operate in order to maintain this activity under the threshold? In this section, we provided empirical arguments in favour of the first "active inhibition hypothesis", but proponents of the "subliminal hypothesis" need to clarify how this activity is maintained at a subthreshold level during motor imagery, thus preventing execution.

\subsection{Inner speech development: Learning not to produce speech}

\cite{watson_psychology_1919} suggested that thought (i.e., covert speech, in his terminology) was rooted in (overt) speech, that is, covert speech matured from overt speech. \cite{vygotsky_thought_1934} then prominently formulated the that inner speech originates in overt speech, and more specifically, in private egocentric speech, that is, self-addressed overt speech in childhood. The idea of speech internalisation and development of inhibition... Vygotsky observed, as Piaget did before, that egocentric or "private" speech tend to be internalised during child development... \cite{fernyhough_alien_2004} extended this model... What if speech internalisation was related to the development of inhibitory abilities?

These ideas could be assessed experimentally in several ways. First, the relation between speech internalisation and inhibitory abilities could be assessed during development at the critical ages (i.e., between 6 and 8 years). We would expect the ability to imagine actions and speech specifically to be positively correlated with inhibitory skills at at this stage...  \cite{wang_relationship_2021} provided correlational evidence that motor imagery and motor inhibition performance improve together between 7 and 11 years old, and that these two abilities correlated at 7 years old (but did not correlate at 11 years old). Second, the inhibitory perspective presented here could be causally assessed by manipulation the inhibitory network preventing execution during motor imagery. For instance, using TMS, can we brake these inhibitory mechanisms and "force" execution during motor imagery... \citep{angelini_motor_2015, angelini_proactive_2016}... Third and finally, inhibition "deficits" in Tourette syndrom...

@@

To sum up, we explored the analogy between covert verbal actions such as covert speech and other forms of motor imagery. This led us to a discussion of two main themes, that is, the question of how the sensory content of motor imagery is produced, and the question of how is it possible for motor imagery not to lead to motor execution. To sketch an answer to these questions, we connected results from the distinct motor imagery, the inner speech, the motor inhibition literature...

@@

\begin{figure}[ht] % float was h! initially
\begin{center}
\includegraphics[width=0.75\textwidth]{figures/inhibitory_triangle.png} % This is a *.eps file
\end{center}
\caption{Plausible neural implementation of the (cortical and subcortical) inhibitory mechanisms responsible for proactive inhibition during motor imagery. The preSMA, the right pIFC, and the STN together form an \textit{inhibitory network} known as the \textit{inhibitory triangle}, which may be responsible for braking motor commands during covert speech production... Created with BioRender.com... FIGURE IN PROGRESS.}\label{fig:2}
\end{figure}

>>>>

\noindent Humans have a remarkable ability to imagine actions without executing them. Such motor imagery is accompanied by a subjective multisensory experience with auditory, visual, and kinaesthetic components. An influential hypothesis states that these sensory percepts result from a simulation of the corresponding motor action that relies on the same internal models recruited for the control of overt actions. A significant consequence of this hypothesis is that the sensory experience of covert actions would be continuously shaped by sensorimotor interactions with the environment. However, the precise computations required by these internal models and their neural implementation remain unclear. Moreover, this simulationnist view raises the question of how it is possible to imagine actions without executing them. In this perspective, we focus on covert verbal actions such as covert speech, writing, or typing, as an exciting case study to help understanding the interplay between language, motor control, and perceptual processes.

@@

\tiny
 \keyFont{\section{Keywords:} motor imagery, motor simulation, motor control, response inhibition, covert speech} % All article types: you may provide up to 8 keywords; at least 5 are mandatory.
\end{abstract}

@@

The ability to mentally examine our thoughts is central to our subjective experience. Mentally anticipating or rehearsing (verbal) actions allows us to become better at performing them \citep[e.g.,][]{toth2020}, to explore/practise novel situations \citep{babar}, or to rehearse past situations \citep{babar}. Broadly construed, motor imagery can be defined as the mental process by which one rehearses an action without engaging in the physical movements involved in this particular action. Because speech production results from sequences of motor commands that are assembled to reach a given communication goal, it belongs to the broader category of motor actions \citep{jeannerod_motor_2006}. Therefore, a parallel can be drawn between covert speech (also known as \textit{inner speech} or \textit{speech imagery}) \citep[for reviews, see][]{alderson-day_inner_2015, perrone-bertolotti_what_2014, loevenbruck_cognitive_2018} and other forms of covert verbal actions such as covert signing, covert writing, or covert typing and, more generally, other imagined actions.

% One of the most influential theoretical model of motor imagery the motor simulation theory \cite{jeannerod_origin_2006, jeannerod_representing_1994, jeannerod_neural_2001}, postulates the existence of a continuum between the covert and the overt execution of an action and that action representations can operate off-line via a simulation mechanism. In short, covert actions would rely on the same set of mechanisms as the overt actions they simulate, except that execution is inhibited \citep{oshea_does_2017}. A second class of models are concerned with the phenomenon of emulation \citep{grush_emulation_2004} and with internal models \cite[for a review of the similarities and dissimilarities between simulation and emulation models, see][]{gentsch_towards_2016}. Internal model theories share the postulate that action control uses internal models, that is, systems that simulate the behaviour of the motor apparatus \citep[e.g.,][]{jordan_forward_1992, kawato_hierarchical_1987}. The function of internal models is to estimate and anticipate the outcome of a motor command. Among the internal model theories, motor control models based on robotic principles \citep[e.g.,][]{kawato_internal_1999, wolpert_internal_1995} assume two kinds of internal models: a forward model (or simulator) that predicts the sensory consequences of motor commands from efference copies of the issued motor commands, and an inverse model (or controller) that calculates the feedforward motor commands from the desired sensory states \citep{gentsch_towards_2016, loevenbruck_cognitive_2018}. Notice that in the following, we do not distinguish further between simulation and emulation, and we use these terms interchangeably to designate the mechanism through which sensory consequences of motor commands (or copy thereof) are computed by forward internal models.

@@

In this perspective, we examine some theoretical and experimental consequences of considering covert verbal actions as inhibited verbal actions. We explore two main themes. First, we discuss the plausible origins of the multisensory (e.g., auditory, kinaesthetic) content of covert verbal actions. Second, we discuss the under-explored role of inhibitory mechanisms during motor imagery and covert verbal actions more specifically. By bridging together recent results from motor imagery, motor inhibition, and inner speech research, we highlight some novel and possibly fruitful lines of research.

@@

Where does the sensory content of covert verbal actions come from? How does motor learning influence the multisensory content of covert verbal actions? In other words, how do the motor and perceptual system interact during covert verbal actions? In the first subsection, we discuss two mechanisms that may be responsible for providing the sensory content of covert verbal actions and their respective involvement in different forms of covert speech. In the second subsection, we discuss an exciting avenue for investigating the influence of motor learning on the sensory content of covert verbal actions, namely, the imagery of totally novel (i.e., never executed) verbal actions.

@@

The production of covert speech is often (although not always and not for everyone) accompanied by the feeling of hearing speech \cite{hurlburt_investigating_2011}. In other words, covert speech is accompanied by a sensory experience that "feels like" hearing speech. In this section, we discuss the dual stream prediction model \citep{tian_mental_2012, tian_effect_2013, tian_mental_2016}, a theoretical account of the mechanisms leading to the generation of such auditory percepts during covert speech, while noticing that these mechanisms could be extended to other covert verbal actions as well.

The dual stream prediction model \citep{tian_mental_2012, tian_effect_2013, tian_mental_2016}... Direct simulation (attention-guided memory retrieval process) or indirect simulation (motor simulation process) \citep{tian_mental_2012, tian_effect_2013, li_corollary_2020, ma_distinct_2019}? The dual stream prediction model \citep{tian_mental_2016}... \citep[similar to the distinction between the prediction-by-simulation or prediction-by-association mechanisms of][]{pickering_integrated_2013}...

The balance between these two mechanisms may depend by the precise instructions given to the participants. For instance, depending on whether participants are instructed to "imagine speaking" or to "imagine hearing" speech (similar to the distinction between the "inner ear" and the "inner voice", e.g., \cite{smith_subvocalization_1992})... Congruent with this hypothesis, it has been shown that inner speaking and inner hearing have distinct MEG correlates and effects on a subsequent /ba/-/ta/ categorisation task \citep{ma_distinct_2019}...

In the absence of non-ambiguous instructions, and in line with \cite{tian_mental_2012}, we suggest that the balance between these two mechanisms may also depend on situational (e.g., surrounding noise) and intrinsic (e.g., expertise) characteristics. For instance... In addition to \cite{tian_mental_2012}, we suggest that a common currency determining the use of one of these mechanisms is the computational cost/resource of each alternative. To clarify, we borrow the concept of memoisation as applied to cognition and mental imagery by \cite{dasgupta_memory_2021}. In this context, memory can be considered as a mechanism to facilitate computational reuse. In the same way... efficient cognition may rely on stored past computation results rather than reinventing the wheel every time. In the context of motor and speech imagery... In other words, situational (extrinsic) and individual (intrinsic) characteristics jointly determine the computational cost (or equivalently, the available computational resources), which in turn determines the balance between the simulation and association mechanisms. Novel and/or difficult tasks may rely more on the simulation mechanism whereas well known tasks may rely more on associative mechanisms... This idea is supported by several studies, showing an increase in facial EMG activity during the reading of difficult text \cite{babar} or while performing difficult mental arithmetic tasks \cite{babar}. See also the discussion in \citep{nalborczyk_understanding_2019-1, nalborczyk_re-analysing_2020}.

Memoisation: avoid redundant computation by storing computational results and reusing them later... functions call are intercepted with by a memoiser the inspects the previous calls of a function and its outputs. If a function has already been called with the same input, then the previously computed output is retrieved and reused... memoisation can be made more flexible (generalisable) by using \textit{interpolation} between cached outputs... for instance, in the context of motor control, reaching a goal (e.g., a cup of tea) can be decomposed in motor primitives, where input-output mapping can be retrieved from a memo table and/or interpolated from sufficiently similar stored mappings... or as put by \cite{dasgupta_memory_2021}, the "shift from algorithm to memory"... this shift is consistent with studies showing a lesser involvement of the motor system for well known imagined actions... Depending on whether the task needs to form "precise" sensory representations and whether we have the time resources to do it... Training studies also suggest that we rely more and more on domain-general (e.g., memory-based) processes with expertise \citep[e.g.,][]{tarr_mental_1989, jolicoeur_time_1985}.

@@

A prediction of this putative mechanism is that the imagination of novel actions, and more precisely, the predicted sensory consequences of novel actions, may be "biased" or "constrained" by the repertoire of already-known actions. This prediction could be assessed by asking participants to imagine a novel action and subsequently checking whether this improves the execution of an intermediate (interpolated) novel action in the articulatory space. The same logic could be applied to the covert production of speech with someone else’s voice. How can we imagine speaking with the voice of our relatives? If it is based on simulators (i.e., on internal models), then the covert production of speech with someone else’s voice should possess sensory properties that are somehow "biased" or "constrained" by the properties of our own sensory and motor systems. Taking as an illustration the auditory sensations of speech, the subjective auditory sensation of covert speech with someone else’s voice should be situated in a somehow intermediate location in the auditory (e.g., formantic) space between the acoustic properties of our own voice and the acoustic properties of someone else voice.

@@

The proposal that overt and covert actions share common neural circuits is faced with a serious problem. If the neural circuits used for the control of overt actions are reused for covert actions, how can covert actions not lead to execution? This puzzle, coined as \textit{the problem of inhibition} by \cite{jeannerod_neural_2001}, can be rephrased as follows: given the putative role of the motor system in providing the multisensory content of motor imagery, how is it possible for motor imagery not to lead to motor execution? In the following, we briefly summarise the evidence in favour of the view of covert verbal actions as inhibited verbal actions. Then, we relate this view with the presumed progressive internalisation of speech during childhood. Finally, we outline some working hypotheses regarding the cognitive and neural implementation of these inhibitory mechanisms.

@@

With regards to covert verbal actions specifically, we hypothesise that they involve an intentional (we know we want to produce motor imagery rather than overt execution) but automatic (we do not explicitly think about not producing movements), planned ahead (proactive), and possibly global form of response inhibition... or maybe both global and effector-specific, cf. the results of \cite{rieger_inhibition_2017}... Notice that the type of motor inhibition that may be at play during motor imagery is still different from the "proactive inhibition" in the motor inhibition literature, in the sense that while doing motor imagery, the participants is not explicitly asked to not produce an action. Instead, they are asked to produce the action \textit{covertly}, which (only implicitly) implies that it should be executed overtly.

Inhibitory mechanisms underlying the ability to imagine actions \citep{guillot_imagining_2012, schwoebel_man_2002}... mentioning the success of BCI with neural activity recorded in premotor/motor areas durmong motor imagery and silent speech... Neural correlates... the inhibitory triangle (cf. Figure \ref{fig:2}), composed of the preSMA, the rIFC, and the STN... A functional dissociation between the preSMA and the rIFC, pause and cancel \citep{diesburg_pause-then-cancel_2021}... Moreover, they also reported a reduced short-interval intracortical inhibition (SICI) in patients with TS, a phenomenon that has been shown to be involved in response inhibition during motor imagery \citep{neige_unravelling_2020}...

Second, the inhibitory perspective presented here could be causally assessed by experimentally manipulating the activity of the inhibitory network responsible for preventing execution during motor imagery. For instance, TMS can be used to "brake" these inhibitory mechanisms and "force" execution during motor imagery... \citep{angelini_motor_2015, angelini_proactive_2016}... Third and finally, inhibition "deficits" in Tourette syndrom... Tourette syndrome is a childhood-onset neurological disorder affecting approximately 1\% of children and characterised by chronic motor and phonic tics (Jackson et al., 2015). Verbal tics can consist of repeating sounds, words, or utterances (palilalia), producing inappropriate or obscene utterances (coprolalia), or the repetition of another’s words (echolalia). Ganos et al. (2014)...  performance during a stop-signal reaction-time task was similar across Tourette patients and healthy controls. However, they observed that the pattern of cerebral activity was different across patients and healthy controls. In their review, Jackson et al. (2015) suggested that increased control over motor outputs is brought about by local increases in GABAergic “tonic” inhibition within re- gions such as the SMA, leading to localised reductions in the gain of motor excitability. Moreover, they also reported a reduced short-interval intracortical inhibition (SICI) in patients with TS, a phenomenon that has been shown to be involved in response inhibition during motor imagery \citep{neige_unravelling_2020}...

Inhibition or subliminal activity/bypassing? \citep{tian_mental_2012, tian_effect_2013, tian_mental_2016} vs. \cite{loevenbruck_cognitive_2018}... However, stating that motor imagery only involve subthreshold activity (and therefore is not accompanied by the emission of motor commands that are inhibited) simply shifts the problem from "how and where motor commands are subsequently inhibited" to "how and where the magnitude of activity in the motor system is planned/regulated/monitored". In other words, we still need to explain how (in a mechanistic and/or developmental way) this activity is maintained at a subthreshold level. What cognitive and neural mechanisms operate in order to maintain this activity under the threshold? In this section, we provided empirical arguments in favour of the "active inhibition hypothesis", but proponents of the "subliminal level hypothesis" need to clarify how this activity is maintained at a subthreshold level during motor imagery, thus preventing execution.

\subsection{Covert speech development: Learning not to produce speech}

\cite{watson_psychology_1919} suggested that thought (i.e., covert speech, in his terminology) was rooted in (overt) speech, that is, covert speech matured from overt speech. \cite{vygotsky_thought_1934} then prominently formulated that covert speech originates in overt speech, and more specifically, in private egocentric speech, that is, self-addressed overt speech in childhood. Vygotsky observed, as Piaget did before, that egocentric or "private" speech tend to be internalised during child development. \cite{fernyhough_alien_2004} extended this model... What if speech internalisation was related to the development of inhibitory abilities? The idea of speech internalisation and development of inhibition...

These ideas could be assessed experimentally in several ways. First, the relation between speech internalisation and inhibitory abilities could be assessed during development at the critical ages (i.e., between 6 and 8 years). We would expect the ability to imagine actions and speech specifically to be positively correlated with inhibitory skills at at this stage...  \cite{wang_relationship_2021} provided correlational evidence that motor imagery and motor inhibition performance improve together between 7 and 11 years old, and that these two abilities correlated at 7 years old (but did not correlate at 11 years old)...

@@

To sum up, we explored the analogy between covert verbal actions such as covert speech and other forms of motor imagery. This led us to a discussion of two main themes, that is, the question of how the sensory content of motor imagery is produced, and the question of how is it possible for motor imagery not to lead to motor execution. To sketch an answer to these questions, we connected results from the motor imagery, motor inhibition, and inner speech research traditions.

@@

\begin{figure}[ht] % float was h! initially
\begin{center}
\includegraphics[width=0.75\textwidth]{figures/inhibitory_triangle.png} % This is a *.eps file
\end{center}
\caption{Plausible neural implementation of the (cortical and subcortical) inhibitory mechanisms responsible for the "proactive" (but implicit) response inhibition at play during motor imagery. The preSMA, right pIFC, and STN together form an \textit{inhibitory network} known as the \textit{inhibitory triangle}, which may be responsible for braking motor commands during covert speech production. Figure created with BioRender.com. FIGURE IN PROGRESS.}\label{fig:2}
\end{figure}
